Below follows the results of the defect estimation as well as the techniques used.

\subsection{Subjective method}
The subjective estimation was only performed by two of the inspectors.
The result of the subjective estimation was as follows:
\begin{itemize}
\item Inspector 1 found 12 defects over the course of two hours and estimated that there was about 25 defects in total, due to his inexperience and probably low detection ability.
\item Inspector 2 found 14 defects over the course of two hours and estimated that there was about 30 defects in total, due to his inexperience and probably low detection ability.
\end{itemize}

\subsection{Capture-recapture method with two inspectors}
During this estimation the \textit{InspectionData} matrix $M_{1}$, described in section~\ref{inspection} was used.
\subsubsection{M0-ML Maximum likelihood}
To make a point estimation of the total amount of defects in the Requirements Document the MatLab file m0mle.m was used with the $M_{1}$ matrix as input. The total amount of defects was estimated to XX.
\subsubsection{Mt-ML Maximum likelihood}
To make a point estimation of the total amount of defects in the Requirements Document the MatLab file mtmle.m was used with the $M_{1}$ matrix as input. The total amount of defects was estimated to XX.
\subsubsection{Mh-JK Jackknife}
To make a point estimation of the total amount of defects in the Requirements Document as well as the confidence interval of the fault content the MatLab file mtmle.m was used with the $M_{1}$ matrix as input. The total amount of defects was estimated to XX and the confidence interval was estimated to XX-XX.

\subsection{Capture-recapture method with four inspectors}
During this estimation the \textit{InspectionData} matrix $M_{2}$, described in section~\ref{inspection} were used.
\subsubsection{M0-ML Maximum likelihood}
To make a point estimation of the total amount of defects in the Requirements Document the MatLab file m0mle.m were used with the $M_{2}$ matrix as input. The total amount of defects was estimated to XX.
\subsubsection{Mt-ML Maximum likelihood}
To make a point estimation of the total amount of defects in the Requirements Document the MatLab file mtmle.m were used with the $M_{2}$ matrix as input. The total amount of defects was estimated to XX.
\subsubsection{Mh-JK Jackknife}
To make a point estimation of the total amount of defects in the Requirements Document as well as the confidence interval of the fault content the MatLab file mtmle.m were used with the $M_{2}$ matrix as input. The total amount of defects was estimated to XX and the confidence interval was XX-XX.